Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal

### 2010-01-20 trunk/doc/msc-proposal/msc-proposal.tex
proposal: added title

\title{IPv6 over Low-Power Wireless Personal Area Networks\\ MSc. Thesis Proposal}
\author{Siarhei Kuryla}

@@

\huge IPv6 over Low-Power Wireless Personal Area Networks\\ [0.5cm]

@@

\chapter{IEEE 802.15.4}\label{ch:ieee802.15.4}
The IEEE 802.15.4 standard \cite{ieee802.15.4} developed by the 802.15.4 Task Group within the IEEE specifies the physical layer and media access control for low-rate wireless personal area networks providing node-to-node frame delivery between devices within reachable distance from each other. The standard is targeted at low cost, low speed and low power consumption devices. This chapter provides an overview of the IEEE 802.15.4 standard.

>>>>

\title{Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ MSc. Thesis Proposal}
\author{Siarhei Kuryla}

@@

\huge Implementation and Evaluation of the Simple Network Management Protocol over IEEE 802.15.4 Radios under the Contiki Operating System\\ [0.5cm]

@@

\chapter{IEEE 802.15.4}\label{ch:ieee802.15.4}
The IEEE 802.15.4 standard developed by the 802.15.4 Task Group within the IEEE specifies the physical layer and media access control for low-rate wireless personal area networks providing node-to-node frame delivery between devices within reachable distance from each other. The standard is targeted at low cost, low speed and low power consumption devices. Several versions of the standard have been published, such as 802.15.4-2003 \cite{ieee802.15.4}, 802.15.4-2006 \cite{ieee802.15.4-2006}, 802.15.4a-2007 \cite{ieee802.15.4a-2007}, 802.15.4c-2009 \cite{ieee802.15.4c-2009} and 802.15.4d-2009 \cite{ieee802.15.4d-2009} . This chapter provides an overview of the IEEE 802.15.4 standard.
